Bioverse: Origins of Life

### 2024-05-28 src/tex/ms.tex
specify distributions in caption
Fig. -> Figure

To determine \gls{HZ} occupancy, we interpolated the stellar luminosity evolution grid of \citet{Baraffe1998} using a Clough Tocher interpolant~\citep[][see left panel of Fig.~\ref{fig:hz_nuv_evo}]{Nielson1983,Alfeld1984} to compute the evolution of the inner (runaway greenhouse) and outer (maximum greenhouse) edges as a function of planet mass and stellar spectral type~\citep{Kopparapu2014}.
This provides each planet's epochs within and outside the \gls{HZ}.
For the \gls{NUV} flux, we use the age- and stellar mass-dependent \gls{NUV} fluxes in the \gls{HZ} obtained by \citet{Richey-Yowell2023}.
We linearly interpolate in their measured grid, where we convert spectral type to stellar mass using the midpoints of their mass ranges (\SI{0.75}{\Msun} for K~stars, \SI{0.475}{\Msun} for early-type M~stars,  and \SI{0.215}{\Msun} for late-type M~stars).
Outside of the age and stellar mass range covered in \citet{Richey-Yowell2023}, we extrapolate using nearest simplex (see right panel of Fig.~\ref{fig:hz_nuv_evo}).

@@

\begin{figure}
    \script{semian_true_evidence.py}
    \begin{centering}
        \includegraphics[width=\hsize]{figures/semian_selectivity.pdf}
        \caption{Scaling of the probability of obtaining true strong evidence with sample selectivity. Left: Sampling distribution for different selectivity parameters $s$. Right: Resulting \mbox{P(true strong evidence)}. Sampling more extreme values of $F_\mathrm{NUV}$ is more likely to yield strong evidence.}
        \label{fig:semian_selectivity}
    \end{centering}
\end{figure}

@@

In a magnitude- and volume-limited sample of a transit survey, the host star distribution will be skewed toward later spectral types and dominated by M~dwarfs (see Fig.~\ref{fig:inhabited_FGKM}).
Due to how the \gls{HZ} scales with spectral type, by far most transiting \glspl{EEC} occur around M~dwarfs.
These host stars, in particular late subtypes, also provide extended periods of increased \gls{NUV} emission that overlap with times when some of these planets occupy the \gls{HZ} (see Fig.~\ref{fig:hz_nuv_evo}), our requirement for abiogenesis (compare Equation~\ref{eq:hypothesis-uv}).
Because of that, all inhabited planets orbit M~dwarfs.

>>>>

To determine \gls{HZ} occupancy, we interpolated the stellar luminosity evolution grid of \citet{Baraffe1998} using a Clough Tocher interpolant~\citep[][see left panel of Figure~\ref{fig:hz_nuv_evo}]{Nielson1983,Alfeld1984} to compute the evolution of the inner (runaway greenhouse) and outer (maximum greenhouse) edges as a function of planet mass and stellar spectral type~\citep{Kopparapu2014}.
This provides each planet's epochs within and outside the \gls{HZ}.
For the \gls{NUV} flux, we use the age- and stellar mass-dependent \gls{NUV} fluxes in the \gls{HZ} obtained by \citet{Richey-Yowell2023}.
We linearly interpolate in their measured grid, where we convert spectral type to stellar mass using the midpoints of their mass ranges (\SI{0.75}{\Msun} for K~stars, \SI{0.475}{\Msun} for early-type M~stars,  and \SI{0.215}{\Msun} for late-type M~stars).
Outside of the age and stellar mass range covered in \citet{Richey-Yowell2023}, we extrapolate using nearest simplex (see right panel of Figure~\ref{fig:hz_nuv_evo}).

@@

\begin{figure}
    \script{semian_true_evidence.py}
    \begin{centering}
        \includegraphics[width=\hsize]{figures/semian_selectivity.pdf}
        \caption{Scaling of the probability of obtaining true strong evidence with sample selectivity. Left: Sampling distribution for different selectivity parameters $s$. Right: Resulting \mbox{P(true strong evidence)} (random, uniform $f_\mathrm{life}$, $F_\mathrm{NUV, min}$). Sampling more extreme values of $F_\mathrm{NUV}$ is more likely to yield strong evidence.}
        \label{fig:semian_selectivity}
    \end{centering}
\end{figure}

@@

In a magnitude- and volume-limited sample of a transit survey, the host star distribution will be skewed toward later spectral types and dominated by M~dwarfs (see Figure~\ref{fig:inhabited_FGKM}).
Due to how the \gls{HZ} scales with spectral type, by far most transiting \glspl{EEC} occur around M~dwarfs.
These host stars, in particular late subtypes, also provide extended periods of increased \gls{NUV} emission that overlap with times when some of these planets occupy the \gls{HZ} (see Figure~\ref{fig:hz_nuv_evo}), our requirement for abiogenesis (compare Equation~\ref{eq:hypothesis-uv}).
Because of that, all inhabited planets orbit M~dwarfs.
